Get Started with `bigsimr` Julia Version

### 2021-02-12 notebooks/bigsimr-julia-getting-started.Rmd
test julia version

---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{tidyverse, patchwork}
---

@@

```{r setup}
library(bigsimr)
library(tidyverse)
library(patchwork)
```

@@

```{r}
(rho <- cor_fast(df, method = "pearson"))
```

@@

```{r}
df %>% select(Temp) %>% summarise_all(.funs = c(mean = mean, sd = sd))
```

@@

```{r}
mle_mean <- function(x) mean(log(x))
mle_sd <- function(x) mean( (log(x) - mean(log(x)))^2 )

df %>% select(Ozone) %>% 
  summarise_all(.funs = c(meanlog = mle_mean, sdlog = mle_sd))
```

@@

```{r}
margins <- alist(
  qlnorm(meanlog = 3.42, sdlog = 0.743),
  qnorm(mean = 77.9, sd = 9.49)
)
```

@@

```{r}
cor_bounds(margins = margins, method = "pearson")
```

@@

```{r}
x <- rvec(10000, rho, margins, "pearson")

df_sim <- as.data.frame(x)
colnames(df_sim) <- colnames(df)
```

@@

>>>>

---
title: "Get Started with `bigsimr` Julia Version"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{tidyverse, patchwork}
---

@@

```{r setup}
## devtools::install_github("SchisslerGroup/bigsimr", ref="julia")
library(bigsimr)
Sys.setenv(JULIA_NUM_THREADS=parallel::detectCores())
## Either let JuliaCall find your installation of Julia or set manually
bs <- bigsimr_setup(JULIA_HOME = "/usr/local/bin/")
dist <- distributions_setup() # Julia distributions
library(tidyverse)
library(patchwork)
```

@@

```{r}
p <- bs$cor(as.matrix(df), bs$Pearson)
p
```

@@

```{r}
mu_temp <- mean(df$Temp)
sd_temp <- sd(df$Temp)
```

@@

```{r}
mu_ozone <- mean(log(df$Ozone))
sd_ozone <- sqrt(mean((log(df$Ozone) - mean(log(df$Ozone)))^2))
```

@@

```{r}
margins <- c(
  dist$Normal(mu_temp, sd_temp),
  dist$LogNormal(mu_ozone, sd_ozone)
)
margins
```

```{r}
D <- bs$MvDistribution(p, margins, bs$Pearson)
D
```

@@

```{r}
bounds <- bs$cor_bounds(D)
bounds$lower
bounds$upper
```

```{r}
bounds <- bs$pearson_bounds(D)
bounds$lower
bounds$upper
```

@@

```{r}
x <- bs$rvec(10000L, p, margins)
head(x)
```

@@

# Pearson matching

## Correlation conversion

```{r}
ps <- bs$cor(as.matrix(df), bs$Spearman)
ps
```

```{r}
bs$cor_bounds(margins[1], margins[2], bs$Spearman)
```

```{r}
D2 <- bs$MvDistribution(ps, margins, bs$Spearman)
x2 <- bs$rand(D2, 1000000L)
bs$cor(x2, bs$Spearman)
```

```{r}
pp <- bs$cor_convert(ps, bs$Spearman, bs$Pearson)
D3 <- bs$MvDistribution(pp, margins, bs$Pearson)
x3 <- bs$rand(D3, 1000000L)
bs$cor(x3, bs$Pearson)
bs$cor(x3, bs$Spearman)
```

```{r}
D4 <- bs$pearson_match(D2);
bs$cor(D4)
```

```{r}
x4 <- bs$rand(D4, 1000000L)
bs$cor(x4, bs$Pearson)
```

```{r}
bs$cor(bs$rand(D, 1000000L))
p
```

```{r}
D5 <- bs$pearson_match(D)
x5 <- bs$rand(D5, 1000000L)
bs$cor(x5)
```

```{r}
m <- as.matrix(brca)
str(m)
```

```{r}
fit_mom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  r <- m^2 / (s^2 - m)
  p <- m / s^2
  dist$NegativeBinomial(r, p)
}
margins <- apply(m, 2, fit_mom)
margins <- do.call(c, unname(margins))
```

```{r}
tau <- bs$cor(m, bs$Spearman)
rho <- bs$cor_convert(tau, bs$Spearman, bs$Pearson)
matrixcalc::is.positive.definite(rho)
```

```{r}
bs$rvec(10L, rho, margins)
```

```{r}
rho_tilde <- bs$cor_nearPD(rho)
matrixcalc::is.positive.definite(rho_tilde)
```

```{r}
x <- bs$rvec(10L, rho_tilde, margins)
str(x)
```
